CLT Results

### 2022-03-30 analysis/clt_data_processing.Rmd
add frequentist model plots

```{r}
write_csv(data,"../data/clt_clean_data")
```

@@

>>>>

```{r}
write_csv(data,"../data/clt_clean_data.csv")
```

@@

```{r}
p1%>%
  mutate(targetWord = factor(targetWord))%>%
  ggplot(., aes(x = reorder(targetWord, -aoa_german_comb), y = mean))+
  geom_hline(yintercept = 0.25, lty = 3, alpha = .75)+
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), alpha = .75)+
  #geom_point( alpha = .75)+
  labs(x = "Item", y = "Proportion correct")+
  ylim(0,1)+
  theme_minimal()+
  coord_flip()
```

### 2022-03-30 analysis/clt_irt_analysis.Rmd
add frequentist model plots

```{r}
irt1 <- brm(
  data = irt_dat,
  family = brmsfamily("bernoulli", "logit"),
  correct ~ 1 + (1 | targetWord) + (1 | subjID),
  prior = prior_1pl,
  cores = 6,
  chains = 6,
  iter = 6000
)

@@

```{r}
irt2 <- brm(
  data = irt_dat,
  family = brmsfamily("bernoulli", "logit"),
  bf(
    correct ~ exp(logalpha) * eta,
    eta ~ 1 + (1 |i| targetWord) + (1 | subjID),
    logalpha ~ 1 + (1 |i| targetWord),
    nl = TRUE
  ),
  prior = prior_2pl,
  cores = 6,
  chains = 6,
  iter = 6000
)

@@

@@

```{r}

beta <- item_pars_3pl_fixed[, , "beta_Intercept"] %>%
  posterior_summary() %>%
	as_tibble() %>%
	rownames_to_column() 
# slopes
alpha <- item_pars_3pl_fixed[, , "logalpha_Intercept"] %>%
  exp() %>%
  sweep(1, person_sds_3pl_fixed, "*") %>%
  posterior_summary() %>%
	as_tibble() %>%
	rownames_to_column()
item_pars_3pl_fixed <- bind_rows(beta, alpha, .id = "nlpar") %>%
	rename(item = "rowname") %>%
	mutate(item = as.numeric(item)) %>%
	mutate(
	  nlpar = factor(nlpar, labels = c("Location", "Slope")),
	  method = "MCMC-H"  
	)

coef_irt3 <- coef(irt3)

@@

```{r}
irt1 <- add_criterion(irt1, "loo") 
irt2 <- add_criterion(irt2, "loo") 
irt3 <- add_criterion(irt3, "loo")

@@

remove <- c("eye", "star", "telephone", "strawberry", "plane" ,"snake" ,"fish" ,"giraffe", "bicycle", "belt", "mushroom", "zebra" ,"kangaroo")

@@

firt1 <- mirt(firt_dat, 1, itemtype = "Rasch")
firt2 <- mirt(firt_dat, 1, itemtype = "2PL")
firt3 <- mirt(firt_dat, 1, itemtype = "3PL")

coef(firt1,
     simplify = T,
     IRTpars = T)

anova(firt1, firt3)

summary(firt_2F)

as_tibble(x$rotF, rownames = "targetWord")%>%
  left_join(aoa)%>%
  ggplot(aes(x = F1, y=F2, col = aoa_german_comb))+
  theme_minimal()+
  geom_point()

coef(firt_2F)

str(x)
```

```{r}
for(i in 1:length(firt_dat)){
  ItemPlot <- itemfit(firt3, 
                      group.bins=15,
                      empirical.plot = i,
                      empirical.CI = .95,
                      method = 'ML') 
  print(ItemPlot)
}
```

>>>>

```{r}
irt1 <- brm(
  data = irt_dat,
  family = brmsfamily("bernoulli", "logit"),
  correct ~ 1 + (1 | targetWord) + (1 | subjID),
  prior = prior_1pl,
  control = list(adapt_delta = 0.9)
  cores = 6,
  chains = 6,
  iter = 6000
)

@@

```{r}
irt2 <- brm(
  data = irt_dat,
  family = brmsfamily("bernoulli", "logit"),
  bf(
    correct ~ exp(logalpha) * eta,
    eta ~ 1 + (1 |i| targetWord) + (1 | subjID),
    logalpha ~ 1 + (1 |i| targetWord),
    nl = TRUE
  ),
  prior = prior_2pl,
  control = list(adapt_delta = 0.9),
  cores = 6,
  chains = 6,
  iter = 6000
)

@@

```{r}
irt3 <- brm(
  data = irt_dat,
  family = brmsfamily("bernoulli", "identity"),
  bf(
    correct ~ 0.25 + 0.75 * inv_logit(exp(logalpha) * eta),
    eta ~ 1 + (1 |i| targetWord) + (1 | subjID),
    logalpha ~ 1 + (1 |i| targetWord),
    nl = TRUE
  ),
  prior = prior_va_3pl,
  control = list(adapt_delta = 0.9),
  cores = 6,
  chains = 6,
  iter = 6000
)

@@

```{r}
coef_irt3 <- coef(irt3)

@@

```{r}
irt1 <- add_criterion(irt1, "loo", moment_match = TRUE) 
irt2 <- add_criterion(irt2, "loo", moment_match = TRUE) 
irt3 <- add_criterion(irt3, "loo", moment_match = TRUE)

@@

remove <- c("eye" ,"telephone" ,"strawberry", "plane" ,"snake" ,"fish", "giraffe", "bicycle" ,"belt")

@@

firt1 <- mirt(firt_dat, 1, itemtype = "Rasch",  guess = .25)
firt2 <- mirt(firt_dat, 1, itemtype = "2PL",  guess = .25)
firt3 <- mirt(firt_dat, 1, itemtype = "3PL",  guess = .25)

anova(firt3,firt2)

summary(firt_2F)
```
```{r}
coefs2PL <- coef(firt2,
     simplify = T,
     IRTpars = T)$items%>%
  as_tibble(rownames = "item")
```

```{r}
traceline <- NULL
for(i in 1:43){
extr.2 <- extract.item(firt2, i)
Theta <- matrix(seq(-6,6, by = .1))
traceline[[i]] <- probtrace(extr.2, Theta)
}

# rename list
names(traceline) <- paste0('item',1:length(traceline))

# rbind traceline
traceline.df <- do.call(rbind, traceline)

# create item names length based on length of theta provided
item <- rep(names(traceline),each=length(Theta))

# put them all together into a dataframe
l.format <- cbind.data.frame(Theta, item, traceline.df)

l.format$item<-as.factor(l.format$item)
aux<-l.format %>%
  group_by(item) %>%
  slice(which.min(abs(P.1-0.5))) # We are only using the P.1 column (dichotomous)

aux<-aux[order(aux$Theta),]
ord<-as.integer(aux$item)
l.format$item = factor(l.format$item,levels(l.format$item)[ord])

names <- irt_dat%>%
  filter(!targetWord %in% remove)%>%
  distinct(targetWord, .keep_all = T)%>%
  select(targetWord)%>%
  mutate(item = paste0("item",row_number()))

format <- l.format%>%left_join(names)

# plot chart
ggplot(format, aes(Theta, P.1)) + 
  geom_line() + 
  #ggtitle('Probability Tracelines') + 
  xlab(expression(theta)) + 
  ylab(expression(P(theta))) + 
  facet_wrap(~targetWord)+
  ylim(0,1)+
  #geom_hline(aes(yintercept = 0.5)) +
  theme_bw() + 
  theme(
        axis.text.x=element_text(colour="black"),
        axis.text.y=element_text(colour="black"),
        legend.title=element_blank())
```
```{r}
plot(firt2, type='trace', which.item = c(1:43), facet_items=T, 
     as.table = TRUE, auto.key=list(points=F, lines=T, columns=4, space = 'top', cex = .8), 
              theta_lim = c(-6, 6), 
     main = "")
```

```{r}
for(i in 1:length(firt_dat)){
  ItemPlot <- itemfit(firt2, 
                      group.bins=15,
                      empirical.plot = i,
                      empirical.CI = .95,
                      method = 'ML') 
  print(ItemPlot)
}
```
